---
title: "p8105_hw5_edm2152"
author: "Eric Morris"
date: "11/6/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(p8105.datasets)
library(rvest)
library(purrr)
```

## Problem 1 

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r, Importing Data}

one_df = 
  tibble(participant = str_c(list.files("./data", full.names = TRUE))) %>% # Getting all file names using list.files
  mutate(long_data = map(participant, read_csv)) %>% # Using map, similar to Napoleon Dynamite Example to read in the data for each subject
  unnest()

one_df_tidy =
  one_df %>% 
  separate(participant, into = c("arm", "id"), sep = "_") %>% 
  separate(arm, into = c("filler1", "arm"), sep = "a/") %>% 
  separate(id, into = c("id", "filler2"), sep = ".c") %>% 
  select(-starts_with("fill")) %>% 
  mutate(arm = str_replace(arm, "con", "control"),
         arm = str_replace(arm, "exp", "experimental"),
         id = as.numeric(id))

```

